### 2023-10-06 2023/certificates/input_for_certificates.tex
update aggregation

\MakeOnePage{Z3++}{\withtrack{Biggest Lead}{\mv}, \withtrack{Largest Contribution}{\mv}}{\withtrack{QF\_LinearIntArith}{\seq,\paral,\sat,\mv}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\sat}}{\withtrack{QF\_IDL}{\unsat}}{s}{}

@@

\MakeOnePage{Bitwuzla}{\withtrack{Biggest Lead}{\inc}}{\withtrack{Bitvec}{\sat}, \withtrack{Equality+MachineArith}{\inc}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Bitvec}{\inc}, \withtrack{QF\_Equality+Bitvec}{\seq,\paral,\sat,\unsat,\fast,\inc,\mv}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc}}{\withtrack{ABVFP}{\sat,\fast}, \withtrack{ABVFPLRA}{\fast}, \withtrack{AUFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{AUFBVFP}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ABVFP}{\uc}, \withtrack{QF\_ABVFPLRA}{\uc}, \withtrack{QF\_BVFP}{\uc}, \withtrack{QF\_BVFPLRA}{\uc}, \withtrack{UFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{UFBVFP}{\seq,\paral,\unsat}}{s}{s}

@@

\MakeOnePage{Q3B}{}{\withtrack{Bitvec}{\fast}}{}{}{}

>>>>

\MakeOnePage{Z3-Z3++}{\withtrack{Biggest Lead}{\mv}, \withtrack{Largest Contribution}{\mv}}{\withtrack{QF\_LinearIntArith}{\seq,\paral,\sat,\mv}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\sat}}{\withtrack{QF\_IDL}{\unsat}}{s}{}

@@

\MakeOnePage{Bitwuzla}{\withtrack{Biggest Lead}{\inc}}{\withtrack{Bitvec}{\sat,\fast}, \withtrack{Equality+MachineArith}{\inc}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Bitvec}{\inc}, \withtrack{QF\_Equality+Bitvec}{\seq,\paral,\sat,\unsat,\fast,\inc,\mv}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc}}{\withtrack{ABVFP}{\sat,\fast}, \withtrack{ABVFPLRA}{\fast}, \withtrack{AUFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{AUFBVFP}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ABVFP}{\uc}, \withtrack{QF\_ABVFPLRA}{\uc}, \withtrack{QF\_BVFP}{\uc}, \withtrack{QF\_BVFPLRA}{\uc}, \withtrack{UFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{UFBVFP}{\seq,\paral,\unsat}}{s}{s}

@@
